???A quantitative framework for investigating the reliability of network construction

### 2017-09-28 manuscript/CI_interactions.tex
learning to use github
formatting error

  \begin{figure}
    \caption{This figure illustrates the upper bound (solid black line) of a 95\% confidence interval for the interaction probability $\lamba$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location. The confidence interval is based on the Clopper-Pearson derivation from the beta distribution. A threshold interaction probability of 0.1 is indicated by the dotted red line.}
    \label{upper_limits}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
  \end{figure}

@@

          If our focal network describes a similar system to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior. The probability of any interaction $L_ij$ depends on the degrees of species $i$ and $j$. The degree of a node is defined as the number of interactions it has with other nodes. Connectance, as the average number of links per species in the whole network, is thus also the expected degree for any given species normalized by the number of species in the network. Using normalized degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i$\times$\Delta_j$. The distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected. We could also use this approach to build a prior distribution using known interaction probabilities for some species in the focal network. The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented. The procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.

@@

    \vspace{12pt}
    \noindent\emph{
       int_probs = c(0.33, 0.09, 0.06, 0.08, 0.42, 0.16, 0.06, 0.38, 0.03, 0.02)
        }.
      \vspace{12pt}

>>>>

  \begin{figure}
    \caption{This figure illustrates the upper bound (solid black line) of a 95\% confidence interval for the interaction probability $\lambda$ when there is no observation of an interaction ($k = 0$) and $n$ observations of the two species co-occurring at a given location. The confidence interval is based on the Clopper-Pearson derivation from the beta distribution. A threshold interaction probability of 0.1 is indicated by the dotted red line.}
    \label{upper_limits}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
  \end{figure}

@@

          If our focal network describes a similar system to that in a known network, we can use the distribution of interaction probabilities in that network to inform our prior. The probability of any interaction $L_ij$ depends on the degrees of species $i$ and $j$. The degree of a node is defined as the number of interactions it has with other nodes. Connectance, as the average number of links per species in the whole network, is thus also the expected degree for any given species normalized by the number of species in the network. Using normalized degrees $\Delta_i$ and $\Delta_j$ (i.e., degrees divided by the number of species in the network), we can obtain the probability of interaction $L_ij$=$\Delta_i\times\Delta_j$. The distribution of these interaction probabilities derived from a similar network or a suite of networks can be used to establish a prior distribution before any data from the focal network are collected. We could also use this approach to build a prior distribution using known interaction probabilities for some species in the focal network. The latter approach allows us to apply information from known, abundant species to the rarest species for which interactions are less frequently documented. The procedure for the estimation of the hyper parameters follows the same approach as described above for connectance except that each measurement is at the individual interaction level instead of the network level.

@@

    \vspace{12pt}
    \noindent\emph{
       int\_probs = c(0.33, 0.09, 0.06, 0.08, 0.42, 0.16, 0.06, 0.38, 0.03, 0.02) }.
      \vspace{12pt}
